Model LF

### 2022-11-02 max_dp endogen stød.Rmd
Commit

prodk_07b = Shock_7b$simulation$prodk
```

```{r}
plot(((unemp_07b - unemp_bs7b)*1000), col= "blue", xlab= "Year", ylab= "Change in unemployment (people)", main= "Change in Unemployment", ylim= c(-300, 3000));
lines(((unemp_04 - unemp_bs4)*1000), col= "black");
lines(((unemp_02 - unemp_bs2)*1000), col= "red");
lines(((unemp_01 - unemp_00)*1000), col= "green");
legend("left", legend=c("All channels except productivity", "insurance rate channel", "wage channel", "demand channel"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","black","red", "green"));
grid()
```

@@

```{r}
plot(((lf_07b - lf_bs7b)*1000), col= "blue", xlab= "Year", ylab= "Change in labor force (people)", main= "Change in Labor force");
grid()
```

>>>>

prod_07b = Shock_7b$simulation$prod
```

```{r}
plot(((unemp_07b - unemp_bs7b)*1000), col= "blue", xlab= "Year", ylab= "Change in unemployment (people)", main= "Change in Unemployment", ylim= c(-300, 3000));
lines(((unemp_04 - unemp_bs4)*1000), col= "black");
lines(((unemp_02 - unemp_bs2)*1000), col= "red");
lines(((unemp_01 - unemp_00)*1000), col= "green");
lines(((unemp_000 - unemp_bs1)*1000), col= "orange");
legend("left", legend=c("All channels except productivity", "insurance rate channel", "wage channel", "demand channel", "LF channel"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","black","red", "green", "orange"));
grid()
```

@@

```{r}
plot(((prod_07b - prod_bs7b)), col= "blue", xlab= "Year", ylab= "Change in labor force (people)", main= "Change in Labor force");
grid()
```
